### 2023-12-13 documentation/thesis/thesis_document.tex
added customizable units

>>>>

\begin{lstlisting}
settings:
 enabled: true
 export_intermediate_results: false
 name: pipeline_analyse_fullsphere

stage import:
 function: import_readings
 parameters:
   IP_input_folder: ./readings/fullsphere/
   IP_file_regex: 360_(.)*.mag.json

stage import_bias_reading:
 function: import_readings
 parameters:
   IP_input_folder: ./readings/fullsphere/
   IP_file_regex: BIAS_(.)*.mag.json

stage apply_bias_offset:
 function: apply_sensor_bias_offset
 parameters:
   bias_readings: stage import_bias_reading
   readings_to_calibrate: stage import

stage plot_normal_bias_offset:
 function: plot_readings
 parameters:
   readings_to_plot: stage apply_bias_offset
   IP_export_folder: ./readings/fullsphere/plots/normal/calibrated/
   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated

stage plot_fullsphere:
 function: plot_fullsphere
 parameters:
   readings_to_plot: stage apply_bias_offset
   IP_export_folder: ./readings/fullsphere/plots/normal/calibrated/
   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated
\end{lstlisting}
